A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-01 deprecated.tex
fix typo and remove tailing space

% related work, trusted IoT trading platform
% MAM -> with IOTA
In the following researches, Masked Authenticated Messaging (MAM) is regarded as a secure data transmission layer and data storage which provides access control, tamperproof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.

@@

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well. The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.

@@

In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authoraized data streams anytime.

% MAM performance
optimizing layers of MAM and compare the performance of different cryptosystems. Furthermore, we take offloading MAM operations to brokers as another solution to reduce the workload of IoT devices, since the brokers are considered to have higher computating power. In Section CITE-TA-SECTION, the security issues and methods of offloading will be discussed carefully.

>>>>

% related work, trusted IoT trading platform
% MAM -> with IOTA
In the following researches, Masked Authenticated Messaging (MAM) is regarded as a secure data transmission layer and data storage which provides access control, tamper-proof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value transactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint.

@@

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well. The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retrieve and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.

@@

In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the disconnection does not exist, participants can retrieve the authorized data streams anytime.

% MAM performance
optimizing layers of MAM and compare the performance of different cryptosystems. Furthermore, we take offloading MAM operations to brokers as another solution to reduce the workload of IoT devices, since the brokers are considered to have higher computational power. In Section CITE-TA-SECTION, the security issues and methods of offloading will be discussed carefully.
